\pkg{Rgbp}: An \proglang{R} Package for Conjugate Gaussian, Poisson, and Binomial Hierarchical Modeling and Frequency Method Checking on Overdispersed Data

### 2015-06-07 jss/article_v2.tex
package and paper

We illustrate our estimation procedure equipped with the adjustment for density maximization (hereafter ADM) \citep{carl1988, morris1997, tang2011}, a distributional approximation to a Pearson family distribution via derivatives, using the Binomial and Poisson hierarchical models. The ADM procedure for the Gaussian hierarchical model used in  \pkg{Rgbp} has been well-documented in \cite{kelly2014advances}.

@@

Obtaining the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$, and those of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ (or $\lambda^E$ for the Poisson model), is the most important estimation problem for the hierarchical models that \code{gbp} assumes. This is because these unconditional posterior moments are used to calculate the unconditional posterior moments of the random effects, $p_1, p_2, \ldots, p_k$ (or $\lambda_1, \lambda_2, \ldots, \lambda_k$ for the Poisson model). Taking the Binomial-Beta model as an example, with the assumption that hyper-parameters $r$ (or $A$ for the Gaussian model) and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ of the Binomial hierarchical model are
\begin{eqnarray}
E(p_{j}\vert \boldsymbol{y}) &=&E(E(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})E(p^E_{j}\vert  \boldsymbol{y})\label{postmean} \\
~~~~~~Var(p_{j}\vert \boldsymbol{y}) &=&  E(Var(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})+Var(E(p_{j}\vert r, \boldsymbol{\beta},\boldsymbol{y})\vert \boldsymbol{y})\label{postvar}\\
&=& E\big(p^{\ast}_{j}(1-p^{\ast}_{j})/ (r+n_{j}+1)\vert  \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big) \\
&\approx&E\big(p^{\ast}_{j}(1-p^{\ast}_{j})(1-\textrm{B}_{j})/n_{i}\vert \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big)\\
&=&g(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}), E(B^3_j\vert\boldsymbol{y}),  E(p^E_{j}\vert\boldsymbol{y}), E((p^E_{j})^2\vert\boldsymbol{y})).\label{approximate_var}
\end{eqnarray}
Note that the unconditional posterior mean and approximate variance of random effect $j$ in Equation \ref{postmean}  and \ref{approximate_var}  are functions of the unconditional posterior moments of shrinkage factors and expected random effects. We specify the function $g$ in Equation \ref{approximate_var} in Appendix \ref{apppostvar}.

We assumed that hyper-parameters $r$ and  $\boldsymbol{\beta}$ were independent a posteriori, considering that they are independent a posteriori in the limit of $k$ going to infinity  because they are asymptotically Normally distributed. 
%Also, \cite{morris1997} used the Poisson model empirically showed that their covariance in observed information matrix of the Poisson-Gamma model was close to 0 in a small sample setting.

For the Poisson model, the unconditional posterior mean and variance of random effect $j$ are
\begin{eqnarray}
E(\lambda_j\vert \boldsymbol{y}) &=&E(E(p_{j}\vert r, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})E(\lambda^E\vert  \boldsymbol{y})\label{postmean_poisson} \\
~~~~~~Var(\lambda_{j}\vert \boldsymbol{y}) &=&  E(Var(p_{j}\vert r,  \boldsymbol{y})\vert \boldsymbol{y})+Var(E(\lambda_{j}\vert r, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_poisson}\\
&=& E\big(\lambda^{\ast}_{j}/ (r+n_{j})\vert  \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-\lambda^E_{j})\vert \boldsymbol{y}\big) \\
&=&h(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}) ).\label{approximate_var_poisson}
\end{eqnarray}
We specify the function $h$ in Equation \ref{approximate_var_poisson} in Appendix \ref{apppostvar_poisson}.
%conditional posterior means of  random effect $j$ in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are a linear function of the shrinkage factor $B_{j}$ and the conditional posterior variances in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are linear (Gaussian), quadratic (Poisson), and  approximately cubic (Binomial) functions of $B_{j}$, considering $r+n_j=n_j/(1-B_j)$.  Thus, the unconditional posterior mean and variance of the random effect are the functions of the unconditional posterior moments of the shrinkage factors.

@@

\subsubsection{Unconditional posterior moments of shrinkage factors.}  It is noted that  the shrinkage factors ($B_1, \ldots B_k$) are a function of $r$, i.e., $B_{j}= r/(r+n_{j})=B_{j}(r)$. One way to approximate the distribution of $B_{j}$ is to find the maximum likelihood estimate of $r$, $\hat{r}_{MLE}$, with its Hessian value and to use a Delta method for an asymptotic Normal distribution of $B_{j}(\hat{r}_{MLE})$. This Normal approximation, however, is defined on $(-\infty, \infty)$ whereas $B_{j}$ lies on the unit interval between 0 and 1, and hence in small sample sizes this approximation can be quite flawed and can even result in point estimates lying on the boundary of the parameter space \citep{tang2011}.

To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of the ADM \citep{carl1988, morris1997, tang2011}. The ADM approximates the distribution of the function of the parameter of interest by one of the Pearson family distributions using the first two derivatives as the MLE with the Delta method does. For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, i.e.,  of $E(B_{j}\vert\boldsymbol{y})$ and $Var(B_{j}\vert\boldsymbol{y})$.  \citet{morris1997} showed that the Beta approximation for the shrinkage factors worked better than Normal approximation in Poisson-Gamma multilevel modeling when the sample size was small, and \citet{tang2011} showed that  in Normal-Normal hierarchical modeling.

The ADM assumes the shrinkage factors follow Beta distributions a posteriori as
\begin{equation}\label{admshrinkage}
B_j\vert\boldsymbol{y}\sim Beta(a_{1j}, a_{0j}), ~\textrm{for}~j=1, 2, \ldots, k,
\end{equation}
%The estimated Beta distribution with the estimates $\hat{a}_{1j}$ and $\hat{a}_{0j}$ will be used to approximate the posterior moments of the shrinkage factors. 
% and $h(B_j)=\log(H(B_j))$Hessian
%whose mean and variance are estimated via two derivatives of an adjusted posterior density and %matched to the two parameters of the Beta distribution, $a_{1j}$ and $a_{0j}$.

@@

ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \cite{berger1999integrated} for the integrated likelihood in detail. Considering that Equation \ref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on $\alpha=-log(r)$ scale because the distribution of $\alpha$ is more symmetric than that of $r$ and $\alpha$ is defined on a real line without any boundary issues. Since $A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto e^\alpha L(\alpha)$, the estimated posterior mean in Equation \ref{admmean} is 
\begin{equation}\label{meaninvariance}
\hat{B}^\ast_j=exp(-\hat{\alpha})/(n_j+exp(-\hat{\alpha})),
\end{equation}

@@

After matching the unconditional posterior mean and variance of shrinkage factor $j$ in Equation \ref{meaninvariance} and \ref{varianceinvariance} to the two parameters of the Beta distribution in Equation \ref{admshrinkage}, i.e., $a_{1j}$ and $a_{0j}$, we get their estimates as
\begin{equation}\label{admpara}
\hat{a}_{1j}=\textrm{inv.info}/(1-\hat{B}^\ast_j)~~\textrm{and}~~\hat{a}_{0j}=\textrm{inv.info}/\hat{B}^\ast_j.
\end{equation}

The moments of the Beta distribution are well defined as a function of $a_{1j}$ and $a_{0j}$; $E(B^c_j\vert\boldsymbol{y})=B(a_{1j} + c, a_{0j})/B(a_{1j}, a_{0j})$ for $c\ge0$. Their estimates are 
\begin{equation}\label{shrinkagemoments}
\widehat{E}(B^c_j\vert\boldsymbol{y})= B(\hat{a}_{1j} + c, \hat{a}_{0j})/B(\hat{a}_{1j}, \hat{a}_{0j}),
\end{equation}

and the approximation gets better if the true posterior distribution of the shrinkage factor is closer to the Beta distribution.

\subsubsection{Unconditional posterior moments of expected random effects for the Binomial model.}
We approximate the unconditional posterior distribution of each expected random effect by the Beta distribution using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$ \citep{carl1988}. A motivation is that the moments of the expected random effects ($p^E_{1}, p^E_{2}, \ldots p^E_{k}$) involve an intractable integration such as
\begin{equation}\label{priormoment1}
E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{e^{x_j^\top\beta}}{1+e^{x_j^\top\beta}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{e^{x_j^\top\beta}}{1+e^{x_j^\top\beta}}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\beta
\end{equation}

Considering that the expected random effects are a function of logistic regression coefficients $\boldsymbol{\beta}$, we can use the Delta method for the asymptotic Normal distribution of $p^E_{j}(\hat{\beta}_{MLE})$. However, the Normal approximation goes through the same support and boundary issues as the shrinkage factors do. Instead, we approximate the posterior distribution of $p^E_{j}(\boldsymbol{\beta})$ by a Beta distribution using $\hat{\beta}_{MLE}$ and the Hessian value at the MLE.

We assume the expected random effect has a Beta distribution a posteriori as follows;
\begin{equation}\label{admpriormean}
p^E_{j}\vert\hat{\alpha}, \boldsymbol{y}=\frac{e^{x_j^\top\beta}}{1+e^{x_j^\top\beta}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\sim \textrm{Beta}(b_{1j}, b_{0j})\sim \frac{G(b_{1j})}{G(b_{1j})+G(b_{0j})},
\end{equation}

where $G(b_{1j})$ is a random variable following a Gamma$(b_{1j}, 1)$ distribution with a unit scale and independently $G(b_{0j})$ has a Gamma($b_{0j}, 1)$ distribution.  Note that the representation in Equation (\ref{admpriormean}) is equivalent to saying $e^{x_j^\top\beta}\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables. Its mean and variance are
\begin{eqnarray}
E(e^{x_j^\top\beta}\vert\hat{\alpha}, \boldsymbol{y})&=&E\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{b_{1j}}{b_{0j}-1}\equiv\eta_j,\label{priormean1}\\
~~~~~Var(e^{x_j^\top\beta}\vert\hat{\alpha}, \boldsymbol{y})&=&Var\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{\eta_j(1+\eta_j)}{b_{0j}-2}.\label{priorvariance1}
\end{eqnarray}

In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ follows $N[\hat{\beta}, \hat{\Sigma}]$, where $\hat{\beta}$ is the mode of $p(\beta\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode. Then the posterior distribution of $x_j^\top\beta$ is also Normal with mean $x_j^\top\hat{\beta}$ and variance $x_j^\top\hat{\Sigma} x_j$.

Using the property of the log-Normal distribution, we get the estimates of posterior mean and variance in Equation (\ref{priormean1}) and (\ref{priorvariance1}) as
\begin{eqnarray}
\eta^\ast_j&=&e^{x_j^\top\hat{\beta}+x_j^\top\hat{\Sigma} x_j/2},\label{priormean2}\\
~~~~~\widehat{Var}(e^{x_j^\top\beta}\vert\boldsymbol{y})&=&\eta^{\ast 2}_j\big(e^{x_j^{T}\hat{\Sigma} x_j}-1\big).\label{priorvariance2}
\end{eqnarray}

By matching the estimated mean and variance in Equation (\ref{priormean2}) and (\ref{priorvariance2}) to $b_{1j}$ and $b_{0j}$ in Equation (\ref{priormean1}) and (\ref{priorvariance1}), we obtain the estimates of $b_{1j}$ and $b_{0j}$ as follows;
\begin{equation}\label{priormeanpara}
\hat{b}_{1j}=\eta^\ast_j+\frac{\eta^\ast_j + 1}{e^{x_j^{T}\hat{\Sigma} x_j}-1}~~\textrm{and}~~\hat{b}_{0j}=\frac{\eta^\ast_j + 1}{\eta^\ast_j(e^{x_j^{T}\hat{\Sigma} x_j}-1)}+2.
\end{equation}

The unconditional posterior moments of expected random effects can be estimated similarly to those of shrinkage factors; since $E((p^E_{j})^d\vert\boldsymbol{y})=B(b_{1j} + d, b_{0j})/B(b_{1j}, b_{0j})$ for $d\ge0$, 
\begin{equation}\label{priormeanmoments}
\widehat{E}((p^E_{j})^d\vert\boldsymbol{y})= B(\hat{b}_{1j} + d, \hat{b}_{0j})/B(\hat{b}_{1j}, \hat{b}_{0j}).
\end{equation}

@@

The unconditional posterior mean and variance for the Binomial model specified in Equation \ref{postmean} and \ref{approximate_var} and those for the Poisson model in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}  are functions of the unconditional posterior moments of shrinkage factors and expected random effect. Once we plug-in the estimated unconditional posterior moments of shrinkage factors in Equation \ref{shrinkagemoments} and those of expected random effect in Equation \ref{priormeanmoments}, we get the estimates of the mean and variance in Equation \ref{postmean}  and \ref{postvar}, i.e., $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively. For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimates of the mean and variance in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}. The estimates of two parameters $t_{1j}$ and $t_{0j}$ in Equation \ref{truebeta} come as follows;
\begin{equation}\label{posttrueprob}
\hat{t}_{1j}=\bigg(\frac{\hat{\mu}_{p_j}(1-\hat{\mu}_{p_j})}{\hat{\sigma}^2_{p_j}}-1\bigg)\hat{\mu}_{p_j},~\textrm{and}~~\hat{t}_{0j}=\bigg(\frac{\hat{\mu}_{p_j}(1-\hat{\mu}_{p_j})}{\hat{\sigma}^2_{p_j}}-1\bigg)(1-\hat{\mu}_{p_j}).
\end{equation}
The estimates of two parameters $s_{1j}$ and $s_{0j}$ in Equation \ref{truebeta_poisson} are
\begin{equation}\label{posttrueprob}
\hat{s}_{1j}=\frac{\hat{\mu}_{\lambda_j}^2}{\hat{\sigma}^2_{\lambda_j}},~\textrm{and}~~\hat{s}_{0j}=\frac{\hat{\mu}_{\lambda_j}}{\hat{\sigma}^2_{\lambda_j}}.
\end{equation}

>>>>

We illustrate our estimation procedure equipped with the adjustment for density maximization (hereafter ADM) \citep{carl1988, morris1997, tang2011}, a way to  approximate a distribution of the parameter of interest by one of Pearson family distributions based on derivatives like the Delta method, using the Binomial and Poisson hierarchical models. The ADM procedure for the Gaussian hierarchical model adopted in  \pkg{Rgbp} has been well-documented in \cite{kelly2014advances}.

@@

Estimating the unconditional posterior moments of the shrinkage factors, $B_1, B_2, \ldots, B_k\equiv r/(r+n_k)$, and the conditional posterior moments of the expected random effects, $p^E_1, p^E_2, \ldots, p^E_k$ (or $\lambda^E$ for the Poisson model), is the most important estimation problem for the hierarchical models that \code{gbp} assumes. This is because these moment estimates are used to approximate the unconditional posterior moments of the random effects, $p_1, p_2, \ldots, p_k$ (or $\lambda_1, \lambda_2, \ldots, \lambda_k$ for the Poisson model). Taking the Binomial-Beta model as an example, with the assumption that hyper-parameters $r$ (or $A$ for the Gaussian model) and $\boldsymbol{\beta}$ are independent a posteriori, the unconditional posterior mean and variance of random effect $j$ are
\begin{eqnarray}
E(p_{j}\vert \boldsymbol{y}) &=&E(E(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})E(p^E_{j}\vert  \boldsymbol{y})\label{postmean} \\
~~~~~~Var(p_{j}\vert \boldsymbol{y}) &=&  E(Var(p_{j}\vert r, \boldsymbol{\beta}, \boldsymbol{y})\vert \boldsymbol{y})+Var(E(p_{j}\vert r, \boldsymbol{\beta},\boldsymbol{y})\vert \boldsymbol{y})\label{postvar}\\
&=& E\big(p^{\ast}_{j}(1-p^{\ast}_{j})/ (r+n_{j}+1)\vert  \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big) \\
&\approx&E\big(p^{\ast}_{j}(1-p^{\ast}_{j})(1-\textrm{B}_{j})/n_{i}\vert \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-p^E_{j})\vert \boldsymbol{y}\big)\\
&=&g(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}), E(B^3_j\vert\boldsymbol{y}),  E(p^E_{j}\vert\boldsymbol{y}), E((p^E_{j})^2\vert\boldsymbol{y})).\label{approximate_var}
\end{eqnarray}
Note that the unconditional posterior mean and approximate variance of random effect $j$ in Equation \ref{postmean}  and \ref{approximate_var}  are functions of the unconditional posterior moments of shrinkage factors and expected random effects. We specify the function $g$ in Equation \ref{approximate_var} in Appendix \ref{apppostvar}.

We assumed that hyper-parameters $r$ and  $\boldsymbol{\beta}$ were independent a posteriori, considering that they are independent a posteriori in the limit of $k$ going to infinity  because they are asymptotically Normally distributed. Also, \cite{morris1997}  empirically showed that their covariance from the observed information matrix of the Poisson-Gamma model, though with a different parametrization, was close to 0 in a small sample setting.

For the Poisson model, the unconditional posterior mean and variance of random effect $j$ are
\begin{eqnarray}
E(\lambda_j\vert \boldsymbol{y}) &=&E(E(p_{j}\vert r, \boldsymbol{y})\vert\boldsymbol{y})=(1-E(B_j\vert\boldsymbol{y}))\bar{y}_j + E(B_j\vert  \boldsymbol{y})\lambda^E\label{postmean_poisson} \\
~~~~~~Var(\lambda_{j}\vert \boldsymbol{y}) &=&  E(Var(p_{j}\vert r,  \boldsymbol{y})\vert \boldsymbol{y})+Var(E(\lambda_{j}\vert r, \boldsymbol{y})\vert \boldsymbol{y})\label{postvar_poisson}\\
&=& E\big(\lambda^{\ast}_{j}/ (r+n_{j})\vert  \boldsymbol{y}\big)+Var\big(\textrm{B}_{j}(\bar{y}_{j}-\lambda^E_{j})\vert \boldsymbol{y}\big) \\
&=&h(E(B_j\vert\boldsymbol{y}), E(B^2_j\vert\boldsymbol{y}) ).\label{approximate_var_poisson}
\end{eqnarray}
The unconditional posterior mean and variance of random effect $j$ under the Poisson model are also functions of the unconditional posterior moments of the shrinkage factors. We specify the function $h$ in Equation \ref{approximate_var_poisson} in Appendix \ref{apppostvar_poisson}.
%conditional posterior means of  random effect $j$ in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are a linear function of the shrinkage factor $B_{j}$ and the conditional posterior variances in Equation  \ref{normalpost}, \ref{gammapost_mean_var}, and \ref{betapost_mean_var} are linear (Gaussian), quadratic (Poisson), and  approximately cubic (Binomial) functions of $B_{j}$, considering $r+n_j=n_j/(1-B_j)$.  Thus, the unconditional posterior mean and variance of the random effect are the functions of the unconditional posterior moments of the shrinkage factors.

@@

\subsubsection{Unconditional posterior moments of shrinkage factors.}  It is noted that  the shrinkage factors ($B_1, \ldots B_k$) are a function of $r$, i.e., $B_{j}= r/(r+n_{j})=B_{j}(r)$. One way to approximate the distribution of $B_{j}$ is to find the maximum likelihood estimate of $r$, $\hat{r}_{MLE}$, with its Hessian value and to use a Delta method for an asymptotic Normal distribution of $B_{j}(\hat{r}_{MLE})$. This Normal approximation, however, is defined on $(-\infty, \infty)$ whereas $B_{j}$ lies on the unit interval between 0 and 1, and hence in small sample sizes this approximation can be quite flawed and can even result in point estimates lying on the boundary of the parameter space, from which the restricted MLE procedure sometimes suffers \citep{tang2011, kelly2014advances}.

To continue with a maximization-based estimation procedure but to steer clear of aforementioned boundary issues we make use of the ADM \citep{carl1988, morris1997, tang2011}. The ADM approximates the distribution of the function of the parameter of interest by one of the Pearson family distributions using the first two derivatives as the Delta method does; the Delta method is a special case of the ADM based on the Normal distribution. For our purposes we approximate the posterior distribution of a shrinkage factor with a Beta distribution, which allows us to finally obtain estimates of the posterior moments, i.e.,  of $E(B_{j}^c\vert\boldsymbol{y})$ for $c\ge0$.  \citet{morris1997} showed that the Beta approximation for the shrinkage factors worked better than Normal approximation using the Poisson hierarchical model when the sample size was small, and \citet{tang2011} showed that  using the Normal hierarchical model.

The ADM assumes that the shrinkage factors follow Beta distributions a posteriori as
\begin{equation}\label{admshrinkage}
B_j\vert\boldsymbol{y}\sim Beta(a_{1j}, a_{0j}), ~\textrm{for}~j=1, 2, \ldots, k,
\end{equation}
and the ADM estimates the two parameters of the Beta distribution, i.e., $a_{1j}$ and $a_{0j}$.
%The estimated Beta distribution with the estimates $\hat{a}_{1j}$ and $\hat{a}_{0j}$ will be used to approximate the posterior moments of the shrinkage factors. 
% and $h(B_j)=\log(H(B_j))$Hessian
%whose mean and variance are estimated via two derivatives of an adjusted posterior density and %matched to the two parameters of the Beta distribution, $a_{1j}$ and $a_{0j}$.

@@

ADM estimates these mean and variance using the marginal posterior distribution of $r$, $f(r\vert\boldsymbol{y})\propto L(r)dr/r^2$, where the marginal likelihood $L(r)=\int L(\boldsymbol{\beta}, r)d\boldsymbol{\beta}$ for the Binomial model is obtained via Laplace approximation with a Lebesque measure on $\boldsymbol{\beta}$ and that for the Poisson model is specified in Equation \ref{marginal_poisson}; see \cite{berger1999integrated} for the integrated likelihood in detail. Considering that Equation \ref{admmean} and  \ref{admvar} involve the maximization and Hessian calculation, we work on a logarithmic scale of $r$, i.e., $\alpha=-log(r)$, because the distribution of $\alpha$ is more symmetric than that of $r$ and $\alpha$ is defined on a real line without any boundary issues. Since $A(B_j\vert\boldsymbol{y})$ is proportional to the marginal posterior density $f(\alpha\vert\boldsymbol{y})\propto e^\alpha L(\alpha)$, the estimated posterior mean in Equation \ref{admmean} is 
\begin{equation}\label{meaninvariance}
\hat{B}^\ast_j=\frac{e^{-\hat{\alpha}}}{n_j+e^{-\hat{\alpha}}},
\end{equation}

@@

After matching the estimated unconditional posterior mean and variance of shrinkage factor $j$ in Equation \ref{meaninvariance} and \ref{varianceinvariance} to the two parameters of the Beta distribution in Equation \ref{admshrinkage}, i.e., $a_{1j}$ and $a_{0j}$, we get their estimates as
\begin{equation}\label{admpara}
\hat{a}_{1j}=\frac{\textrm{inv.info}}{1-\hat{B}^\ast_j}~~\textrm{and}~~\hat{a}_{0j}=\frac{\textrm{inv.info}}{\hat{B}^\ast_j}.
\end{equation}

The moments of the Beta distribution are well defined as a function of $a_{1j}$ and $a_{0j}$; $E(B^c_j\vert\boldsymbol{y})=B(a_{1j} + c, a_{0j})/B(a_{1j}, a_{0j})$ for $c\ge0$. Their estimates are 
\begin{equation}\label{shrinkagemoments}
\widehat{E}(B^c_j\vert\boldsymbol{y})= \frac{B(\hat{a}_{1j} + c, \hat{a}_{0j})}{B(\hat{a}_{1j}, \hat{a}_{0j})},
\end{equation}

and the approximation gets better if the true posterior distribution of the shrinkage factor is closer to the Beta distribution \citep{morris1997, tang2011, morris2012}.

\subsubsection{Unconditional posterior moments of expected random effects for the Binomial model.}
We assume that the conditional posterior distribution of each expected random effect given $\hat{\alpha}$ follows a Beta distribution, and estimate the assumed Beta distribution using the first and second derivatives of the conditional posterior distribution of $\beta$ given $\hat{\alpha}$. We estimate the conditional posterior moments of the expected random effects and treat them as their estimated unconditional posterior moments obtained by the (Laplace) approximate marginal likelihood function of $\boldsymbol{\beta}$. We found that the conditional and unconditional posterior moment estimates were almost identical due to their small covariance between $r$ and $\boldsymbol{\beta}$ in the observed information matrix. In addition, calculating the conditional posterior moments was computationally less burdensome.

The moments of the expected random effects ($p^E_{1}, p^E_{2}, \ldots p^E_{k}$) involve an intractable integration. For example, the first conditional posterior moment is
\begin{equation}\label{priormoment1}
E(p^E_{j}\vert\hat{\alpha}, \boldsymbol{y})=E\bigg(\frac{e^{x_j^\top\boldsymbol{\beta}}}{1+e^{x_j^\top\boldsymbol{\beta}}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\bigg)=\int_{\mathbf{R}^{m}} \frac{e^{x_j^\top\boldsymbol{\beta}}}{1+e^{x_j^\top\boldsymbol{\beta}}}f(\beta\vert\hat{\alpha}, \boldsymbol{y})d\boldsymbol{\beta}.
\end{equation}

Considering that the expected random effects are a function of logistic regression coefficients $\boldsymbol{\beta}$, we can use the Delta method for the asymptotic Normal distribution of $p^E_{j}(\hat{\boldsymbol{\beta}}_{MLE})$. However, the Normal approximation goes through the same support and boundary issues as the shrinkage factors do. Instead, we approximate the conditional posterior distribution of $p^E_{j}(\boldsymbol{\beta})$ by a Beta distribution using $\hat{\beta}_{MLE}$ and the Hessian value at the MLE.

We assume the conditional posterior distribution of expected random effect $j$ is a Beta distribution as follows;
\begin{equation}\label{admpriormean}
p^E_{j}\vert\hat{\alpha}, \boldsymbol{y}=\frac{e^{x_j^\top\boldsymbol{\beta}}}{1+e^{x_j^\top\boldsymbol{\beta}}}\bigg\vert\hat{\alpha}, \boldsymbol{y}\sim \textrm{Beta}(b_{1j}, b_{0j})\sim \frac{G(b_{1j})}{G(b_{1j})+G(b_{0j})},
\end{equation}

where $G(b_{1j})$ is a random variable following a Gamma$(b_{1j}, 1)$ distribution with a unit scale and independently $G(b_{0j})$ has a Gamma($b_{0j}, 1)$ distribution.  Note that the representation in Equation (\ref{admpriormean}) is equivalent to saying $e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y}\sim G(b_{1j})/G(b_{0j})$, a ratio of two independent Gamma random variables. Its mean and variance are
\begin{eqnarray}
E(e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y})&=&E\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{b_{1j}}{b_{0j}-1}\equiv\eta_j,\label{priormean1}\\
~~~~~Var(e^{x_j^\top\boldsymbol{\beta}}\vert\hat{\alpha}, \boldsymbol{y})&=&Var\bigg(\frac{G(b_{1j})}{G(b_{0j})}\bigg)=\frac{\eta_j(1+\eta_j)}{b_{0j}-2}.\label{priorvariance1}
\end{eqnarray}

In order to estimate $b_{1j}$ and $b_{0j}$, we assume that the conditional posterior distribution of $\beta$ follows $N[\hat{\beta}, \hat{\Sigma}]$, where $\hat{\boldsymbol{\beta}}$ is the mode of $p(\boldsymbol{\beta}\vert \hat{\alpha}, \boldsymbol{y})$  and $\hat{\Sigma}$ is a negative Hessian matrix at the mode. Then the posterior distribution of $x_j^\top\boldsymbol{\beta}$ is also Normal with mean $x_j^\top\hat{\boldsymbol{\beta}}$ and variance $x_j^\top\hat{\Sigma} x_j$.

Using the property of the log-Normal distribution, we get the estimates of posterior mean and variance in Equation (\ref{priormean1}) and (\ref{priorvariance1}) as
\begin{eqnarray}
\hat{\eta}_j&=&e^{x_j^\top\hat{\boldsymbol{\beta}}+x_j^\top\hat{\Sigma} x_j/2},\label{priormean2}\\
~~~~~\widehat{Var}(e^{x_j^\top\boldsymbol{\beta}}\vert\boldsymbol{y})&=&\hat{\eta}^2_j\big(e^{x_j^{T}\hat{\Sigma} x_j}-1\big).\label{priorvariance2}
\end{eqnarray}

By matching the estimated mean and variance in Equation (\ref{priormean2}) and (\ref{priorvariance2}) to $b_{1j}$ and $b_{0j}$ in Equation (\ref{priormean1}) and (\ref{priorvariance1}), we obtain the estimates of $b_{1j}$ and $b_{0j}$ as follows;
\begin{equation}\label{priormeanpara}
\hat{b}_{1j}=\hat{\eta}_j+\frac{\hat{\eta}_j + 1}{e^{x_j^{T}\hat{\Sigma} x_j}-1}~~\textrm{and}~~\hat{b}_{0j}=\frac{\hat{\eta}_j + 1}{\hat{\eta}_j(e^{x_j^{T}\hat{\Sigma} x_j}-1)}+2.
\end{equation}

The conditional posterior moments of expected random effects can be estimated similarly to those of shrinkage factors;  $E((p^E_{j})^d\vert\hat{\alpha}, \boldsymbol{y})=B(b_{1j} + d, b_{0j})/B(b_{1j}, b_{0j})$ for $d\ge0$. Finally, we estimate the unconditional posterior moments of expected random effects by their estimated conditional posterior moments as follows.
\begin{equation}\label{priormeanmoments}
\widehat{E}((p^E_{j})^d\vert\boldsymbol{y})= \frac{B(\hat{b}_{1j} + d, \hat{b}_{0j})}{B(\hat{b}_{1j}, \hat{b}_{0j})}.
\end{equation}

@@

The unconditional posterior mean and variance of each random effect for the Binomial model specified in Equation \ref{postmean} and \ref{approximate_var} and those for the Poisson model in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}  are functions of the unconditional posterior moments of shrinkage factors and expected random effect. Once we plug-in the estimated unconditional posterior moments of shrinkage factors in Equation \ref{shrinkagemoments} and those of expected random effect in Equation \ref{priormeanmoments}, we get the estimates of the unconditional posterior mean and variance of each random effect in Equation \ref{postmean}  and \ref{postvar} denoted by $\hat{\mu}_{p_j}$ and $\hat{\sigma}^2_{p_j}$, respectively. For the Poisson model, let  $\hat{\mu}_{\lambda_j}$ and $\hat{\sigma}^2_{\lambda_j}$ denote the estimates of the unconditional posterior mean and variance in Equation \ref{postmean_poisson} and \ref{approximate_var_poisson}. The estimates of two parameters $t_{1j}$ and $t_{0j}$ in Equation \ref{truebeta} come as follows;
\begin{equation}\label{posttrueprob}
\hat{t}_{1j}=\bigg(\frac{\hat{\mu}_{p_j}(1-\hat{\mu}_{p_j})}{\hat{\sigma}^2_{p_j}}-1\bigg)\hat{\mu}_{p_j},~\textrm{and}~~\hat{t}_{0j}=\bigg(\frac{\hat{\mu}_{p_j}(1-\hat{\mu}_{p_j})}{\hat{\sigma}^2_{p_j}}-1\bigg)(1-\hat{\mu}_{p_j}).
\end{equation}
The estimates of two parameters $s_{1j}$ and $s_{0j}$ in Equation \ref{truebeta_poisson} are
\begin{equation}\label{posttrueprob}
\hat{s}_{1j}=\frac{\hat{\mu}_{\lambda_j}^2}{\hat{\sigma}^2_{\lambda_j}},~\textrm{and}~~\hat{s}_{0j}=\frac{\hat{\mu}_{\lambda_j}}{\hat{\sigma}^2_{\lambda_j}}.
\end{equation}
